---
title: "Experiment Status Quo Applications"
subtitle: "Analysis July 19"
author: "Omar Vasquez Duque"
  
output:
  bookdown::pdf_book:
    dev: cairo_pdf
    keep_tex:  true
fontsize: 11pt
toc: false

header-includes:
   - \setlength\parindent{24pt}
   - \usepackage{float}
   - \usepackage{flafter}
   - \usepackage{pdflscape}
   - \usepackage{rotating}
---


```{r include=FALSE}
library(readr)
library(janitor)
library(extrafont)
library(extrafontdb)
library(Cairo)
loadfonts()
library(tidyverse)

source('Theme_Publication.R')

df <- read_csv("Search+Prolific_July+12,+2023_22.29.csv") # Experiment 1

dat <- read_csv("Search+Prolific+July+13_July+14,+2023_14.23.csv") # Experiment 2

options(scipen=999)

```
# Data cleaning

First experiment. July 13, 2023. Prolific. Sample of 300 people. Second experiment, July 14, 2023. Sample of 400 people.
```{r include=FALSE}

# Data cleaning for first and second experiment (df = first, dat = second)

df = df %>% 
  clean_names() %>% 
    slice(-c(1,2)) # first two rows repeat var names 

dat = dat %>% 
  clean_names() %>% 
    slice(-c(1,2)) # first two rows repeat var names 

```

```{r include=FALSE}

#More cleaning

df = df %>% 
  filter(consent ==1, #filters out did not consent
         distribution_channel == "anonymous", # filters out previews
         q14 == "5", # attention check
         q15 == "7", # bot check
         !is.na(app_cupertino)) # filters out incompletes

dat = dat %>% 
  filter(consent ==1, #filters out did not consent
         distribution_channel == "anonymous", # filters out previews
         q14 == "5", # attention check
         q15 == "7",
         !is.na(q37))# bot check

```


```{r include=FALSE}
# filter responses too quick and too slow 

df$duration_in_seconds = as.numeric(df$duration_in_seconds) # changes var type

median_completion = median(df$duration_in_seconds) # creates median variable

df2 = df %>% 
  filter(duration_in_seconds >= 0.5 * median_completion & duration_in_seconds <=1.75*median_completion) # n lowers to 257

dat$duration_in_seconds = as.numeric(dat$duration_in_seconds) # changes var type

median_completion2 = median(dat$duration_in_seconds) # creates median variable

dat2 = dat %>% 
  filter(duration_in_seconds >= 0.5 * median_completion2 & duration_in_seconds <=1.75*median_completion2) # n does not change

```

```{r include=FALSE}
# Create treatment vars

df2 = df2 %>% 
  mutate(choice_search = ifelse(survey_version == "1", 1, 0),
         default_search = ifelse(survey_version == "2", 1, 0),
         choice_weather = ifelse(survey_type_weather == "1", 1,0),
         default_weather = ifelse(survey_type_weather == "2", 1, 0))


mean(df2$choice_search) # good balance

mean(df2$default_search) # sanity check. All good

#'* Does not apply to second experiment (only default condition)*
```

## var creation for analysis 

```{r include=FALSE}
# Create vars for search experiment

dfexp = df2 %>% 
  mutate(chose_google = if_else(choice_screen == 1, 1, 0, NULL),
         chose_duckduckgo = if_else(choice_screen == 2,1,0, NULL),
         chose_bing = if_else(choice_screen == 3, 1,0, NULL),
         chose_ecosia = if_else(choice_screen == 4, 1, 0, NULL),
         chose_yahoo = if_else(choice_screen == 5,1,0, NULL),
         
         choice = factor(case_when(chose_google == 1 ~ "Google",
                            chose_bing == 1 ~ "Bing",
                            chose_duckduckgo == 1 ~ "DuckDuck Go",
                            chose_ecosia == 1 ~ "Ecosia",
                            chose_yahoo == 1 ~ "Yahoo"),
                         levels = c("Google", 
                                    "Bing", 
                                    "DuckDuck Go", 
                                    "Ecosia", 
                                    "Yahoo")),
         
         assigned_google = ifelse(default_assigned=="1",1,0),
         assigned_bing = ifelse(default_assigned=="2",1,0),
         assigned_duckduckgo = ifelse(default_assigned=="4",1,0),
         assigned_yahoo = ifelse(default_assigned=="3",1,0),
         
         used_google_q1 = if_else(grepl("1", se_beatles), 1, 0, NULL),
         used_duckduckgo_q1 = if_else(grepl("4", se_beatles),1,0,NULL),
         used_bing_q1 = if_else(grepl("2", se_beatles),1,0,NULL),
         used_yahoo_q1 = if_else(grepl("3", se_beatles),1,0,NULL),
         used_other_q1 = if_else(grepl("5", se_beatles),1,0,NULL),
         
         used_google_q2 = if_else(grepl("1", se_alcapone), 1, 0, NULL),
         used_duckduckgo_q2 = if_else(grepl("4", se_alcapone),1,0,NULL),
         used_bing_q2 = if_else(grepl("2", se_alcapone),1,0,NULL),
         used_yahoo_q2 = if_else(grepl("3", se_alcapone),1,0,NULL),
         used_other_q2 = if_else(grepl("5", se_alcapone),1,0,NULL),
         
         used_google_q3 = if_else(grepl("1", se_vangogh), 1, 0, NULL),
         used_duckduckgo_q3 = if_else(grepl("4", se_vangogh),1,0,NULL),
         used_bing_q3 = if_else(grepl("2", se_vangogh),1,0,NULL),
         used_yahoo_q3 = if_else(grepl("3", se_vangogh),1,0,NULL),
         used_other_q3 = if_else(grepl("5", se_vangogh),1,0,NULL),
         
         just_one_sq1 = ifelse(str_length(se_beatles)==1, 1,0),
         just_one_sq2 = ifelse(str_length(se_alcapone)==1, 1,0),
         just_one_sq3 = ifelse(str_length(se_vangogh)==1, 1,0),

         google_qual = q60_1,
         bing_qual = q60_2,
         ddg_qual = q60_3,
         yahoo_qual = q60_5,
         
         google_prior = ifelse(grepl("1", q58), 1, 0),
         ddg_pior = ifelse(grepl("2", q58),1, 0),
         bing_prior = ifelse(grepl("3", q58), 1, 0),
         ecosia_prior = ifelse(grepl("4", q58), 1, 0),
         yahoo_prior = ifelse(grepl("5", q58), 1, 0),
         other_prior = ifelse(grepl("6", q58), 1, 0),
         across(starts_with("assigned"), as.factor), # transform all assign vars to factors
         across(ends_with("qual"), as.numeric),
         forced_choice_s = as.factor(choice_search),
         forced_choice_w = as.factor(choice_weather)) # the same but for numeric )
         
     
```

## var creation second exp

```{r include=FALSE}

# The same for second experiment

datexp = dat2 %>% 
  mutate(assigned_google = ifelse(fl_12_do == "Google_default",1,0),
         assigned_bing = ifelse(fl_12_do == "Bing_default",1,0),
         video = ifelse(fl_90_do == "Video",1,0),
         
         used_google_q1 = if_else(grepl("1", se_beatles), 1, 0, NULL),
         used_duckduckgo_q1 = if_else(grepl("4", se_beatles),1,0,NULL),
         used_bing_q1 = if_else(grepl("2", se_beatles),1,0,NULL),
         used_yahoo_q1 = if_else(grepl("3", se_beatles),1,0,NULL),
         used_other_q1 = if_else(grepl("5", se_beatles),1,0,NULL),
         
         used_google_q2 = if_else(grepl("1", se_alcapone), 1, 0, NULL),
         used_duckduckgo_q2 = if_else(grepl("4", se_alcapone),1,0,NULL),
         used_bing_q2 = if_else(grepl("2", se_alcapone),1,0,NULL),
         used_yahoo_q2 = if_else(grepl("3", se_alcapone),1,0,NULL),
         used_other_q2 = if_else(grepl("5", se_alcapone),1,0,NULL),
         
         used_google_q3 = if_else(grepl("1", se_vangogh), 1, 0, NULL),
         used_duckduckgo_q3 = if_else(grepl("4", se_vangogh),1,0,NULL),
         used_bing_q3 = if_else(grepl("2", se_vangogh),1,0,NULL),
         used_yahoo_q3 = if_else(grepl("3", se_vangogh),1,0,NULL),
         used_other_q3 = if_else(grepl("5", se_vangogh),1,0,NULL),
         
         used_google_q4 = if_else(grepl("1", q58_55), 1, 0, NULL),
         used_duckduckgo_q4 = if_else(grepl("4", q58_55),1,0,NULL),
         used_bing_q4 = if_else(grepl("2", q58_55),1,0,NULL),
         used_yahoo_q4 = if_else(grepl("3", q58_55),1,0,NULL),
         used_other_q4 = if_else(grepl("5", q58_55),1,0,NULL),
         
         used_google_q5 = if_else(grepl("1", q60), 1, 0, NULL),
         used_duckduckgo_q5 = if_else(grepl("4", q60),1,0,NULL),
         used_bing_q5 = if_else(grepl("2", q60),1,0,NULL),
         used_yahoo_q5 = if_else(grepl("3", q60),1,0,NULL),
         used_other_q5 = if_else(grepl("5", q60),1,0,NULL),
         
         just_one_sq1 = ifelse(str_length(se_beatles)==1, 1,0),
         just_one_sq2 = ifelse(str_length(se_alcapone)==1, 1,0),
         just_one_sq3 = ifelse(str_length(se_vangogh)==1, 1,0),
         just_one_sq4 = ifelse(str_length(q58_55)==1, 1,0),
         just_one_sq5 = ifelse(str_length(q60)==1, 1,0),
         
         google_qual = q60_1,
         bing_qual = q60_2,
         ddg_qual = q60_3,
         yahoo_qual = q60_5,
         
         google_prior = ifelse(grepl("1", q58_66), 1, 0),
         ddg_pior = ifelse(grepl("2", q58_66),1, 0),
         bing_prior = ifelse(grepl("3", q58_66), 1, 0),
         ecosia_prior = ifelse(grepl("4", q58_66), 1, 0),
         yahoo_prior = ifelse(grepl("5", q58_66), 1, 0),
         other_prior = ifelse(grepl("6", q58_66), 1, 0),
         across(starts_with("assigned"), as.factor), # transform all assign vars to factors
         across(ends_with("qual"), as.numeric))
         
```


```{r}
table(dfexp$choice)

table(dfexp$assigned_bing)
```
# Exploratory analysis

# search engine choice plot

```{r echo=FALSE, warning=FALSE}

# Check coding is correct with visualizations

dfexp %>% 
  filter(choice_search==1) %>% 
  ggplot(aes(x=choice, fill = choice)) +
  geom_bar(alpha = 0.7) +
  scale_fill_discrete(drop=FALSE) + #to show columns with zeros
          scale_x_discrete(drop=FALSE) + #to show columns with zeros
  # theme_Publication() +
  scale_fill_brewer(palette = "Set2") +
  theme_Publication() +
  theme(text = element_text(family = "LM Roman 10"))
```


```{r}

# test = dfexp %>% 
#   mutate(across(starts_with("used"), as.numeric)) 

#' *This worked!!! Saves a lot of time. Mind I should use "across" much more. And apply, lapply, sapply too.*

# test = test %>% 
#   mutate(nbing = used_bing_q1 + used_bing_q2 + used_bing_q3) # This works too!
```

## creates dfs for comparison pA|D(A) vs pA|C

```{r}
# Create dfs for comparison with forced choice

dfgoogle = dfexp %>% 
  filter(forced_choice_s==1 | assigned_google==1) 

dfbing = dfexp %>% 
  filter(forced_choice_s==1 | assigned_bing==1) 

dfyahoo = dfexp %>% 
  filter(forced_choice_s==1 | assigned_yahoo==1) 

dfddg = dfexp %>% 
  filter(forced_choice_s==1 | assigned_duckduckgo==1) 

```


```{r}
library(jtools)
```

Mind there are two ways to operationalize the effect: 

1) compared with choice-screen

2) compared with any other default



## creates df for default condition 

```{r}
# DF for defaults in search
dfexp_def_s = dfexp %>% 
  filter(choice_search==0)
```

# Status Quo Effects Search

## Bing
```{r}
# Bing Q1
sqbingq1= glm(used_bing_q1 ~ forced_choice_s, data=dfbing, family ="binomial")

#check effect on quality

qualbing = lm(bing_qual ~ forced_choice_s, data = dfbing)

summary(qualbing)

plotbingq1 = effect_plot(sqbingq1, pred = "forced_choice_s", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotbingq1
```


*Interesting. Status quo effect goes down. People start switching. I need longer questionnaire. Hopefully, 5 enough. If not, run final version with 7 questions? Not sure it's worth it

*Different comparison: Pb|B compared with any other default

```{r}

lm(data = dfexp, used_bing_q1 ~ assigned_bing)

lm(data = dfexp, used_bing_q1 ~ assigned_bing + bing_qual + bing_prior) #It is working this time! Gather larger n too. But quality and prior use are correlated and my sample is not 

bingq1 = glm(data = dfexp_def_s, used_bing_q1 ~ assigned_bing: bing_prior, family = "binomial")

summary(bingq1)

typeof(dfexp$bing_qual)

lm(data = dfexp, used_bing_q3 ~ assigned_bing)
```

```{r}
#'* Second experiment*
lm(data = datexp, used_bing_q1 ~ assigned_bing)

e2.test = lm(data = datexp, used_bing_q1 ~ assigned_bing:bing_prior + bing_qual)
summary(e2.test) #there is an interaction effect. Prior use moderates the effect of the default

e2.bingq1 = glm(data = datexp, used_bing_q1 ~ assigned_bing + bing_prior, family = "binomial")

summary(e2.bingq1)

#'*visualization*
# E2. Bing Q1
e2.sqbingq1= glm(used_bing_q1 ~ assigned_bing, data=datexp, family ="binomial")

e2.plotbingq1 = effect_plot(e2.sqbingq1, pred = "assigned_bing", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

e2.plotbingq1
```

Now, do the same for Q5

```{r}
e2.sqbingq5= glm(used_bing_q5 ~ assigned_bing, data=datexp, family ="binomial")

e2.plotbingq5 = effect_plot(e2.sqbingq5, pred = "assigned_bing", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

e2.plotbingq5
```

See how this effect affects Google

## Video had no effect. Probably everyone pais attention. Check number of correct answers

See if video had an effect... It did not work out. No difference
```{r}
# Creates status quo variable (for Q1)
datexp = datexp %>% 
  mutate(statquo = ifelse(assigned_bing ==1 & used_bing_q1==1 | assigned_google ==1 & used_google_q1==1, 1,0),
         video = as.factor(video))

mean(datexp$statquo)

datbing = datexp %>% 
  filter(assigned_bing==1) # New DF to compare just those assigned to Bing

glmvideo = glm(data=datexp, formula=statquo ~ video, family = "binomial")

summary(glmvideo)



glm.video = effect_plot(glmvideo, pred = "video", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

glm.video

```


```{r}
e2.googleq5= glm(used_google_q5 ~ assigned_bing, data=datexp, family ="binomial")

e2.plotgoogleq5 = effect_plot(e2.googleq5, pred = "assigned_bing", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

e2.plotgoogleq5
```
Substantial effect! lowers use of Google! 




```{r}
#Bing Q3

sqbingq3= glm(used_bing_q3 ~ forced_choice_s, data=dfbing, family ="binomial")

plotbingq3 = effect_plot(sqbingq3, pred = "forced_choice_s", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotbingq3
```

## Yahoo

Check status quo effects for Yahoo. There is no variance, so just report counts

```{r}
sqyahooq1= glm(used_yahoo_q1 ~ forced_choice_s, data=dfyahoo, family ="binomial")


plotyahooq1 = effect_plot(sqyahooq1, pred = "forced_choice_s", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")


#Now check for default data: pY|Y vs pY|Y`

sqdefyahooq1 = glm(used_yahoo_q1 ~ assigned_yahoo, data=dfexp_def_s, family ="binomial")

plotsqdefyahooq1 = effect_plot(sqdefyahooq1, pred = "assigned_yahoo", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

# Check q3

sqdefyahooq3 = glm(used_yahoo_q3 ~ assigned_yahoo, data=dfexp_def_s, family ="binomial")

plotsqdefyahooq3 = effect_plot(sqdefyahooq3, pred = "assigned_yahoo", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotyahooq1

plotsqdefyahooq1

plotsqdefyahooq3
```

## DuckDuck Go

Do the same with DuckDuckGo

```{r}
sqdefddg1 = glm(used_duckduckgo_q1 ~ assigned_duckduckgo, data=dfexp_def_s, family ="binomial")

plotsqdefddg1 = effect_plot(sqdefddg1, pred = "assigned_duckduckgo", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotsqdefddg1
# Check q3

sqdefddgq3 = glm(used_duckduckgo_q3 ~ assigned_duckduckgo, data=dfexp_def_s, family ="binomial")

plotsqdefddgq3 = effect_plot(sqdefddgq3, pred = "assigned_duckduckgo", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotsqdefddgq3

```



```{r}
sqyahooq3= glm(used_yahoo_q3 ~ forced_choice_s, data=dfyahoo, family ="binomial")

plotyahooq3 = effect_plot(sqyahooq3, pred = "forced_choice_s", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotyahooq3
```
Compare with other defaults. Do chi-squared test. 

```{r}

yahooq1 = glm(data = dfexp_def_s, used_yahoo_q1 ~ assigned_yahoo + yahoo_prior, family = "binomial")

summary(yahooq1)

lm(data = dfexp_def_s, used_yahoo_q1 ~ assigned_yahoo + yahoo_prior + yahoo_qual)
```

## Big regression general analysis status quo effect

There si something wrong with the default data set. Showing NAs in assigned to a

```{r}
dfexp_def_s = dfexp_def_s %>% 
  mutate(statquo_sq1 = ifelse(assigned_bing==1 & used_bing_q1==1 | assigned_google==1 & used_google_q1==1 | assigned_duckduckgo==1 & used_duckduckgo_q1==1 | assigned_yahoo==1 & used_yahoo_q1==1, 1, 0),
         statquo_sq3= ifelse(assigned_bing==1 & used_bing_q3==1 | assigned_google==1 & used_google_q3==1|assigned_duckduckgo==1 & used_duckduckgo_q3==1 | assigned_yahoo==1 & used_yahoo_q3==1, 1, 0),
         prior_use = ifelse(assigned_google==1 & google_prior==1 | assigned_bing==1 & bing_prior==1 | assigned_duckduckgo==1 & ddg_pior==1 | assigned_yahoo==1 & yahoo_prior==1,1,0),
         explor_sq1 = ifelse(str_length(se_beatles)>1, 1,0),
         age = 2023 - as.numeric(q32),
         age_c = case_when(age<30 ~ "18-29",
                           age >29 & age <40 ~ "30-39",
                           age >39 & age <50 ~ "40-49",
                           age>49 & age <60 ~ "50-59",
                           age>59 ~ "60 +"))


lm(data=dfexp_def_s, formula= statquo_sq1 ~  prior_use)

lm(data=dfexp_def_s, formula= statquo_sq1 ~ prior_use + age_c)

```
Data defaults without Google

```{r}
dfexp_def_s2 = dfexp_def_s %>% 
  filter(assigned_google==0)
```


```{r}
lm(data=dfexp_def_s2, formula= statquo_sq1 ~ explor_sq1 + prior_use)

glmsqs1 = glm(data=dfexp_def_s2, formula= statquo_sq1 ~ explor_sq1 + prior_use, family = "binomial")

summary(glmsqs1)
```
Interesting coefficients, qualitatively. Now, run glm because p>1

```{r}
mean(dfexp_def_s$statquo_sq1) 
```

## Check if those who use the default use another one too!

This is important. q1 only a few use more than one, q3 many more explore. 

```{r}
# Create var for analysis

dfexp_def_s = dfexp_def_s %>% 
  mutate(se_assigned = case_when(assigned_google==1 ~ "Google",
                                 assigned_bing==1 ~ "Bing",
                                 assigned_duckduckgo==1 ~"DuckDuck Go",
                                 assigned_yahoo==1 ~ "Yahoo"))
```

Code below irrelevant. q1 only one person used more than one 
```{r}
# glm_just_one= glm(just_one_sq1 ~ se_assigned, data=dfexp_def_s, family ="binomial")
# 
# plot_just_one_sq1 = effect_plot(glm_just_one, pred = "se_assigned", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")
# 
# plot_just_one_sq1

table(dfexp_def_s$se_assigned, dfexp_def_s$just_one_sq1)

table(dfexp_def_s$se_assigned, dfexp_def_s$just_one_sq2)

table(dfexp_def_s$se_assigned, dfexp_def_s$just_one_sq3)
```
Code above is not what I need. The relevant variable is stat_quo_qi * just_one_qi

```{r}
dfexp_def_s = dfexp_def_s %>% 
  mutate(just_default_sq1 = ifelse(statquo_sq1==1 & just_one_sq1==1,1,0),
         just_default_sq3 = ifelse(statquo_sq3==1 & just_one_sq3==1,1,0))
```

```{r}
table(dfexp_def_s$se_assigned, dfexp_def_s$just_default_sq1)

table(dfexp_def_s$se_assigned, dfexp_def_s$just_default_sq3)
```
### Now with the second experiment

```{r}
datexp = datexp %>% 
  mutate(se_assigned = case_when(assigned_google==1 ~ "Google",
                                 assigned_bing==1 ~ "Bing"),
         statquo_sq1 = ifelse(assigned_bing==1 & used_bing_q1==1 | assigned_google==1 & used_google_q1==1, 1, 0),
         statquo_sq2 = ifelse(assigned_bing==1 & used_bing_q2==1 | assigned_google==1 & used_google_q2==1, 1, 0),
         statquo_sq3= ifelse(assigned_bing==1 & used_bing_q3==1 | assigned_google==1 & used_google_q3==1, 1, 0),
         statquo_sq4 = ifelse(assigned_bing==1 & used_bing_q4==1 | assigned_google==1 & used_google_q4==1, 1, 0),
         statquo_sq5 = ifelse(assigned_bing==1 & used_bing_q5==1 | assigned_google==1 & used_google_q5==1, 1, 0),
         prior_use = ifelse(assigned_google==1 & google_prior==1 | assigned_bing==1 & bing_prior==1,1,0),
         just_default_sq1 = ifelse(statquo_sq1==1 & just_one_sq1==1,1,0),
         just_default_sq2 = ifelse(statquo_sq2==1 & just_one_sq3==1,1,0),
         just_default_sq3 = ifelse(statquo_sq3==1 & just_one_sq3==1,1,0),
         just_default_sq4 = ifelse(statquo_sq4==1 & just_one_sq3==1,1,0),
         just_default_sq5 = ifelse(statquo_sq5==1 & just_one_sq3==1,1,0))
```


```{r}
table(datexp$se_assigned, datexp$just_default_sq1)

table(datexp$se_assigned, datexp$just_default_sq2)

table(datexp$se_assigned, datexp$just_default_sq3)

table(datexp$se_assigned, datexp$just_default_sq4)

table(datexp$se_assigned, datexp$just_default_sq5)
```
Interesting result. More people tend to use Bing exclusively over time.

# Results Weather Apps

```{r}

# The same for weather apps part

dfexp2 = dfexp %>% 
  mutate(chose_wc = if_else(choice_screen_2 == 1, 1, 0, NULL),
         chose_aw = if_else(choice_screen_2 == 2,1,0, NULL),
         chose_wu = if_else(choice_screen_2 == 3, 1,0, NULL),
         
         choice_wa = factor(case_when(chose_wc == 1 ~ "Weather Channel",
                            chose_aw == 1 ~ "AccuWeather",
                            chose_wu == 1 ~ "Weather Underground"),
                         levels = c("Weather Channel", 
                                    "AccuWeather", 
                                    "WeatherUnderground")),
         
         assigned_wc = ifelse(weather_do %in% "default_wc", 1, 0), 
         assigned_aw = ifelse(weather_do %in% "default_aw", 1, 0),
         assigned_wu = ifelse(weather_do %in% "default_wu", 1, 0),
         
         used_wc_q1 = if_else(grepl("1", app_austin), 1, 0, NULL),
         used_aw_q1 = if_else(grepl("2", app_austin),1,0,NULL),
         used_wu_q1 = if_else(grepl("3", app_austin),1,0,NULL),
         used_other_q1 = if_else(grepl("4", app_austin),1,0,NULL),
         
         used_wc_q2 = if_else(grepl("1", app_cambridge), 1, 0, NULL),
         used_aw_q2 = if_else(grepl("2", app_cambridge),1,0,NULL),
         used_wu_q2 = if_else(grepl("3", app_cambridge),1,0,NULL),
         
         used_wc_q3 = if_else(grepl("1", app_cupertino), 1, 0, NULL),
         used_aw_q3 = if_else(grepl("2", app_cupertino),1,0,NULL),
         used_wu_q3 = if_else(grepl("3", app_cupertino),1,0,NULL),

         ac_qual = q31_1,
         aw_qual = q31_2,
         wu_qual = q31_3,
         
         ac_prior = ifelse(grepl("1", q54), 1, 0),
         aw_pior = ifelse(grepl("2", q54),1, 0),
         wu_prior = ifelse(grepl("3", q54), 1, 0),
         other_prior = ifelse(grepl("4", q54), 1, 0))
         
         
```


```{r}
dfaw = dfexp2 %>% 
  filter(forced_choice_w==1| assigned_aw==1) 
  

```

One plot for sq q1 for each (a1_q1, a2_q1, a3_q1)

Another for sq q3 for each (a1_q3, a2_q3, a3_q3)

```{r}

#AccuWeather
sqawq1= glm(used_aw_q1 ~ forced_choice_w, data=dfaw, family ="binomial")

plotawq1 = effect_plot(sqawq1, pred = "forced_choice_w", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotawq1

```

```{r}

sqawq3= glm(used_aw_q3 ~ forced_choice_w, data=dfaw, family ="binomial")

plotawq3 = effect_plot(sqawq3, pred = "forced_choice_w", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotawq3

```

```{r}

# Convert vars for analysis

test = dfexp2 %>% 
  mutate(across(starts_with("used"), as.numeric)) 

#' *This worked!!! Saves a lot of time. Mind I should use "across" much more. And apply, lapply, sapply too.*

test = test %>% 
  mutate(nbing = used_bing_q1 + used_bing_q2 + used_bing_q3) # This works too!


```

```{r}

```

Effect_plot to show correlations browsers/s.engines controlling for changes in OSX market shares



