---
title: "Prolific Data"
author: "OVD"
date: "2023-07-13"
output: pdf_document
---

```{r}
library(readr)
library(janitor)
library(extrafont)
library(extrafontdb)
library(Cairo)
loadfonts()
library(tidyverse)

df <- read_csv("Search+Prolific_July+12,+2023_22.29.csv")

```

```{r}

# Data cleaning

df = df %>% 
  clean_names() %>% 
    slice(-c(1,2)) # first two rows repeat var names 

df = df %>% 
  filter(consent ==1, #filters out did not consent
         !is.na(prolific_id), # filters out previews
         q14 == "5", # attention check
         q15 == "7", # bot check
         !is.na(app_cupertino)) # filters out incompletes

typeof(df$q14)
# filter responses too quick and too slow 

df$duration_in_seconds = as.numeric(df$duration_in_seconds) # changes var type

median_completion = median(df$duration_in_seconds) # creates median variable

df2 = df %>% 
  filter(duration_in_seconds >= 0.5 * median_completion & duration_in_seconds <=1.75*median_completion) # n lowers to 257


```

```{r}
# Treatment vars

df2 = df2 %>% 
  mutate(choice_search = ifelse(survey_version == "1", 1, 0),
         default_search = ifelse(survey_version == "2", 1, 0),
         choice_weather = ifelse(survey_type_weather == "1", 1,0),
         default_weather = ifelse(survey_type_weather == "2", 1, 0))

mean(df2$choice_search) # good balance

mean(df2$default_search) # sanity check. All good
```


```{r}

# Add additional vars for experiment search engines

dfexp = df2 %>% 
  mutate(chose_google = if_else(choice_screen == 1, 1, 0, NULL),
         chose_duckduckgo = if_else(choice_screen == 2,1,0, NULL),
         chose_bing = if_else(choice_screen == 3, 1,0, NULL),
         chose_ecosia = if_else(choice_screen == 4, 1, 0, NULL),
         chose_yahoo = if_else(choice_screen == 5,1,0, NULL),
         
         choice = factor(case_when(chose_google == 1 ~ "Google",
                            chose_bing == 1 ~ "Bing",
                            chose_duckduckgo == 1 ~ "DuckDuck Go",
                            chose_ecosia == 1 ~ "Ecosia",
                            chose_yahoo == 1 ~ "Yahoo"),
                         levels = c("Google", 
                                    "Bing", 
                                    "DuckDuck Go", 
                                    "Ecosia", 
                                    "Yahoo")),
         
         assigned_google = ifelse(default_assigned=="1",1,0),
         assigned_bing = ifelse(default_assigned=="2",1,0),
         assigned_duckduckgo = ifelse(default_assigned=="4",1,0),
         assigned_yahoo = ifelse(default_assigned=="3",1,0),
         
         used_google_q1 = if_else(grepl("1", se_beatles), 1, 0, NULL),
         used_duckduckgo_q1 = if_else(grepl("4", se_beatles),1,0,NULL),
         used_bing_q1 = if_else(grepl("2", se_beatles),1,0,NULL),
         used_yahoo_q1 = if_else(grepl("3", se_beatles),1,0,NULL),
         used_other_q1 = if_else(grepl("5", se_beatles),1,0,NULL),
         
         used_google_q2 = if_else(grepl("1", se_alcapone), 1, 0, NULL),
         used_duckduckgo_q2 = if_else(grepl("4", se_alcapone),1,0,NULL),
         used_bing_q2 = if_else(grepl("2", se_alcapone),1,0,NULL),
         used_yahoo_q2 = if_else(grepl("3", se_alcapone),1,0,NULL),
         used_other_q2 = if_else(grepl("5", se_alcapone),1,0,NULL),
         
         used_google_q3 = if_else(grepl("1", se_vangogh), 1, 0, NULL),
         used_duckduckgo_q3 = if_else(grepl("4", se_vangogh),1,0,NULL),
         used_bing_q3 = if_else(grepl("2", se_vangogh),1,0,NULL),
         used_yahoo_q3 = if_else(grepl("3", se_vangogh),1,0,NULL),
         used_other_q3 = if_else(grepl("5", se_vangogh),1,0,NULL),

         google_qual = q60_1,
         bing_qual = q60_2,
         ddg_qual = q60_3,
         yahoo_qual = q60_5,
         
         google_prior = ifelse(grepl("1", q58), 1, 0),
         ddg_pior = ifelse(grepl("2", q58),1, 0),
         bing_prior = ifelse(grepl("3", q58), 1, 0),
         ecosia_prior = ifelse(grepl("4", q58), 1, 0),
         yahoo_prior = ifelse(grepl("5", q58), 1, 0),
         other_prior = ifelse(grepl("6", q58), 1, 0),
         across(starts_with("assigned"), as.factor), # transform all assign vars to factors
         across(ends_with("qual"), as.numeric),
         forced_choice = as.factor(choice_search),
         forced_choice2 = as.factor(choice_weather)) # the same but for numeric )
         
         
         
```

```{r}
table(dfexp$choice)

table(dfexp$assigned_bing)
```

```{r}
source('Theme_Publication.R')
# Check coding is correct with visualizations

dfexp %>% 
  filter(choice_search==1) %>% 
  ggplot(aes(x=choice, fill = choice)) +
  geom_bar(alpha = 0.7) +
  scale_fill_discrete(drop=FALSE) + #to show columns with zeros
          scale_x_discrete(drop=FALSE) + #to show columns with zeros
  # theme_Publication() +
  scale_fill_brewer(palette = "Set2") +
  theme_Publication() +
  theme(text = element_text(family = "LM Roman 10"))
```

```{r}

test = dfexp2 %>% 
  mutate(across(starts_with("used"), as.numeric)) 

#' *This worked!!! Saves a lot of time. Mind I should use "across" much more. And apply, lapply, sapply too.*

test = test %>% 
  mutate(nbing = used_bing_q1 + used_bing_q2 + used_bing_q3) # This works too!
```



```{r}
# Create dfs for comparison with forced choice

dfgoogle = dfexp %>% 
  filter(forced_choice==1 | assigned_google==1) 

dfbing = dfexp %>% 
  filter(forced_choice==1 | assigned_bing==1) 

dfyahoo = dfexp %>% 
  filter(forced_choice==1 | assigned_yahoo==1) 

dfddg = dfexp %>% 
  filter(forced_choice==1 | assigned_duckduckgo==1) 

```


```{r}
library(jtools)
```

Mind there are two ways to operationalize the effect: 

1) compared with choice-screen

2) compared with any other default

```{r}
# Bing Q1
sqbingq1= glm(used_bing_q1 ~ forced_choice, data=dfbing, family ="binomial")

plotbingq1 = effect_plot(sqbingq1, pred = "forced_choice", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotbingq1
```


*Interesting. Status quo effect goes down. People start switching. I need longer questionnaire. Hopefully, 5 enough. If not, run final version with 7 questions? Not sure it's worth it

*Different comparison: Pb|B compared with any other default

```{r}

# DF for defaults
dfexp_def = dfexp %>% 
  filter(forced_choice==0 | forced_choice2==0)

lm(data = dfexp, used_bing_q1 ~ assigned_bing)

lm(data = dfexp, used_bing_q1 ~ assigned_bing + bing_qual + bing_prior) #It is working this time! Gather larger n too. But quality and prior use are correlated and my sample is not 

bingq1 = glm(data = dfexp_def, used_bing_q1 ~ assigned_bing + bing_prior, family = "binomial")

summary(bingq1)

typeof(dfexp$bing_qual)

lm(data = dfexp, used_bing_q3 ~ assigned_bing)

```



```{r}
#Bing Q3

sqbingq3= glm(used_bing_q3 ~ forced_choice, data=dfbing, family ="binomial")

plotbingq3 = effect_plot(sqbingq3, pred = "forced_choice", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotbingq3
```

Check status quo effects for Yahoo

```{r}
sqyahooq1= glm(used_yahoo_q1 ~ forced_choice, data=dfyahoo, family ="binomial")

plotyahooq1 = effect_plot(sqyahooq1, pred = "forced_choice", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotyahooq1
```

```{r}
sqyahooq3= glm(used_yahoo_q3 ~ forced_choice, data=dfyahoo, family ="binomial")

plotyahooq3 = effect_plot(sqyahooq3, pred = "forced_choice", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotyahooq3
```
Compare with other defaults. Do chi-squared test. 

```{r}

yahooq1 = glm(data = dfexp_def, used_yahoo_q1 ~ assigned_yahoo + yahoo_prior, family = "binomial")

summary(yahooq1)

lm(data = dfexp_def, used_yahoo_q1 ~ assigned_yahoo + yahoo_prior + yahoo_qual)
```



```{r}

# The same for weather apps part

dfexp2 = dfexp %>% 
  mutate(chose_wc = if_else(choice_screen_2 == 1, 1, 0, NULL),
         chose_aw = if_else(choice_screen_2 == 2,1,0, NULL),
         chose_wu = if_else(choice_screen_2 == 3, 1,0, NULL),
         
         choice_wa = factor(case_when(chose_wc == 1 ~ "Weather Channel",
                            chose_aw == 1 ~ "AccuWeather",
                            chose_wu == 1 ~ "Weather Underground"),
                         levels = c("Weather Channel", 
                                    "AccuWeather", 
                                    "WeatherUnderground")),
         
         assigned_wc = ifelse(weather_do %in% "default_wc", 1, 0), 
         assigned_aw = ifelse(weather_do %in% "default_aw", 1, 0),
         assigned_wu = ifelse(weather_do %in% "default_wu", 1, 0),
         
         used_wc_q1 = if_else(grepl("1", app_austin), 1, 0, NULL),
         used_aw_q1 = if_else(grepl("2", app_austin),1,0,NULL),
         used_wu_q1 = if_else(grepl("3", app_austin),1,0,NULL),
         used_other_q1 = if_else(grepl("4", app_austin),1,0,NULL),
         
         used_wc_q2 = if_else(grepl("1", app_cambridge), 1, 0, NULL),
         used_aw_q2 = if_else(grepl("2", app_cambridge),1,0,NULL),
         used_wu_q2 = if_else(grepl("3", app_cambridge),1,0,NULL),
         
         used_wc_q3 = if_else(grepl("1", app_cupertino), 1, 0, NULL),
         used_aw_q3 = if_else(grepl("2", app_cupertino),1,0,NULL),
         used_wu_q3 = if_else(grepl("3", app_cupertino),1,0,NULL),

         ac_qual = q31_1,
         aw_qual = q31_2,
         wu_qual = q31_3,
         
         ac_prior = ifelse(grepl("1", q54), 1, 0),
         aw_pior = ifelse(grepl("2", q54),1, 0),
         wu_prior = ifelse(grepl("3", q54), 1, 0),
         other_prior = ifelse(grepl("4", q54), 1, 0))
         
         
```


```{r}
dfaw = dfexp2 %>% 
  filter(forced_choice2==1| assigned_aw==1) 
  

```


```{r}

#AccuWeather
sqawq1= glm(used_aw_q1 ~ forced_choice2, data=dfaw, family ="binomial")

plotawq1 = effect_plot(sqawq1, pred = "forced_choice2", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotawq1

```

```{r}
plotawq3 = effect_plot(sqawq3, pred = "forced_choice2", interval = TRUE, plot.points = TRUE, jitter = c(0.2, 0.01), point.alpha = 0.4, colors = "Qual1")

plotawq3

sqawq3= glm(used_aw_q3 ~ forced_choice2, data=dfaw, family ="binomial")
```

```{r}

# Convert vars for analysis

test = dfexp2 %>% 
  mutate(across(starts_with("used"), as.numeric)) 

#' *This worked!!! Saves a lot of time. Mind I should use "across" much more. And apply, lapply, sapply too.*

test = test %>% 
  mutate(nbing = used_bing_q1 + used_bing_q2 + used_bing_q3) # This works too!


```

```{r}

```

